|

### 2020-05-28 paper/Manuscript.Rmd

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    affiliation: "3,4"
  - name: "Aaron Peikert"
    affiliation: "3,5"
  - name: "Barbara Vreede"
    affiliation: "6"
  - name: "Anna-Lena Lamprecht"
    affiliation: "2,7"
    email: "a.l.lamprecht@uu.nl"
  - name: "Loek Brinkman"
    affiliation: "2,8"
  - name: "Marijn E. Struiksma"
    affiliation: "2,9"

<!-- I would suggest to put OSCU as last item in the list of affiliations, as it is complementary to the primary institutional affiliations --> 
affiliation:
  - id: "1"
    institution: "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id: "2" 
    institution: "Open Science Community Utrecht"
  - id: "3"
    institution: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id: "4"
    institution: "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK"
  - id: "5"
    institution: "Humboldt-Universitaet zu Berlin"
  - id: "6"
    institution: "University Library Utrecht"
  - id: "7"
    institution: "Utrecht University, Department of Information and Computing Sciences"
  - id: "8"
    institution: "UMC Utrecht"
  - id: "9"
    institution: "Utrecht Institute of Linguistics OTS"

>>>>

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    affiliation: "3,4"
  - name: "Aaron Peikert"
    affiliation: "3,5"
  - name: "Barbara Vreede"
    affiliation: "6"
  - name: "Anna-Lena Lamprecht"
    affiliation: "2,7"
    email: "a.l.lamprecht@uu.nl"
  - name: "Loek Brinkman"
    affiliation: "2,8"
  - name: "Marijn E. Struiksma"
    affiliation: "2,9"
    email: "m.struiksma@uu.nl"

<!-- I would suggest to put OSCU as last item in the list of affiliations, as it is complementary to the primary institutional affiliations --> 
affiliation:
  - id: "1"
    institution: "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id: "2" 
    institution: "Open Science Community Utrecht"
  - id: "3"
    institution: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id: "4"
    institution: "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK"
  - id: "5"
    institution: "Humboldt-Universitaet zu Berlin"
  - id: "6"
    institution: "University Library Utrecht"
  - id: "7"
    institution: "Utrecht University, Department of Information and Computing Sciences"
  - id: "8"
    institution: "UMC Utrecht"
  - id: "9"
    institution: "Utrecht University, Department of Language, Literature & Communication, Utrecht Institute of Linguistics OTS"
